Quantum Magic Games

### 2023-07-03 paper/main.tex
paper => up to magic arrangement

\usepackage[table]{xcolor}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{nicefrac}
\usepackage{hhline}
\usepackage{bigdelim}
\usepackage{booktabs}

@@

\section{Characterizing Quantum Magic Games}
\label{sec:extending}
What if we change the format of the Mermin-Peres magic square game?
Maybe increase the number of rows and columns, or even change the
shape entirely? Figure~\ref{fig:as-graph} (a) gives an example of the
magic pentagram game, in which the product of the labels (\(+1\) or
\(-1\)) assigned to each of four vertices in a line must equal the
labels of that line (the product of the four vertices in the topmost
horizontal line, for example, must be \(-1\)). Notice that we are now
changing the visualization format to
hypergraphs. Figure~\ref{fig:as-graph} (b) shows the magic square as a
hypergraph. In this section, we explore a characterization of games that
follow the same style as the magic square and pentagram, given
by~\ref{arkhipov2012}.

\begin{figure}[htbp]
  \centering
  \begin{subfigure}[t]{0.49\textwidth}
    \begin{center}
      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
        \node (00) [vertex] at (-1.25, 0) {};
        \node (01) [vertex] at (0,  0) {};
        \node (02) [vertex] at (1.25,  0) {};

@@

        (20) edge (21)
        (21) edge (22)
        ;
      \end{tikzpicture}
    \end{center}
    \caption{The magic square game as a hypergraph.}
  \end{subfigure}
  \hfill{}
   \begin{subfigure}[t]{0.49\textwidth}
    \begin{center}
      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
        \foreach \c [evaluate=\c as \ang using {18 + 72*\c}] in {0, 1, 2, 3, 4} {
          \node [vertex] (\c) at (\ang:25mm) {};
        }

        \node [text=red!50!black!80] (label0--2) at ($(01)!0.5!(12) - (0, 0.25)$) {\(-1\)};
        \node [text=green!50!black!80] (label1--4) at ($(01)!0.5!(04) + (-0.3, -0.1)$) {\(+1\)};
        \node [text=green!50!black!80] (label0--3) at ($(04)!0.5!(34) + (-0.1, 0.25)$) {\(+1\)};
        \node [text=green!50!black!80] (label2--4) at ($(23)!0.5!(34) + (+0.1, 0.25)$) {\(+1\)};
        \node [text=green!50!black!80] (label1--3) at ($(12)!0.5!(23) + (+0.3, -0.1)$) {\(+1\)};
      \end{tikzpicture}
    \end{center}
    \caption{The pentagram game as a hypergraph.}
  \end{subfigure}
  \caption{Examples of hypergraphs representing quantum magic games~\ref{arkhipov2012}.}
\end{figure}
\printbibliography{}
\end{document}

>>>>

\usepackage[table]{xcolor}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{nicefrac}
\usepackage{hhline}
\usepackage{bigdelim}
\usepackage{booktabs}

@@

\section{Characterizing Quantum Magic Games}
\label{sec:extending}
What if we change the format of the Mermin-Peres magic square game?
Maybe increase the dimensions, or even change the shape entirely?
Figure~\ref{fig:as-graph} (a) gives an example of the magic pentagram
game, in which the product of the labels (\(\pm{}1\)) assigned to each
of four vertices in a line must equal the labels of that line (the
product of the four vertices in the topmost horizontal line, for
example, must be \(-1\)). Notice that we are now changing the
visualization format to hypergraphs.  Figure~\ref{fig:as-graph} (b)
shows the magic square as a hypergraph.  As the magic square, the
pentagram is also due to Mermin~\ref{xxx}.  In this section, we
explore a characterization of Mermin-style games, given
by~\cite{arkhipov2012}.

\begin{figure}[htbp]
  \centering
   \begin{subfigure}[t]{0.49\textwidth}
    \begin{center}
      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
        \foreach \c [evaluate=\c as \ang using {18 + 72*\c}] in {0, 1, 2, 3, 4} {
          \node [vertex] (\c) at (\ang:25mm) {};
        }

        \node [text=red!50!black!80] (label0--2) at ($(01)!0.5!(12) - (0, 0.25)$) {\(-1\)};
        \node [text=green!50!black!80] (label1--4) at ($(01)!0.5!(04) + (-0.3, -0.1)$) {\(+1\)};
        \node [text=green!50!black!80] (label0--3) at ($(04)!0.5!(34) + (-0.1, 0.25)$) {\(+1\)};
        \node [text=green!50!black!80] (label2--4) at ($(23)!0.5!(34) + (+0.1, 0.25)$) {\(+1\)};
        \node [text=green!50!black!80] (label1--3) at ($(12)!0.5!(23) + (+0.3, -0.1)$) {\(+1\)};
      \end{tikzpicture}
    \end{center}
    \caption{The pentagram game as a hypergraph.}
  \end{subfigure}
  \hfill{}
  \begin{subfigure}[t]{0.49\textwidth}
    \begin{center}
      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
        \node (00) [vertex] at (-1.25, 0) {};
        \node (01) [vertex] at (0,  0) {};
        \node (02) [vertex] at (1.25,  0) {};

@@

        (20) edge (21)
        (21) edge (22)
        ;
      \end{tikzpicture}
    \end{center}
    \caption{The magic square game as a hypergraph.}
  \end{subfigure}
  \caption{Examples of hypergraphs representing quantum magic games~\cite{arkhipov2012}.\label{fig:as-graph}}
\end{figure}

We start by defining the notion of \emph{arrangements}, which are
configurations on which Mermin-style games may be
played. \cite{arkhipov2012} defines both unsigned and signed
arrangements. Instead, we shall focus  on \emph{signed}
arrangements, and thus anytime we say ``arrangement'' we mean the
signed version.

\begin{definition}[Arrangement~\cite{arkhipov2012}]\label{def:arrangement}
  An arrangement \(A = (V, E, \ell)\) is a finite connected hypergraph
  with vertex set \(V\) and hyperedge set \(E\), where a hyperedge is
  a nonempty subset of \(V\), such that every vertex \(v \in V\) lies
  in exactly two hyperedges \(e_{0}, e_{1} \in E\) (\emph{connected}
  means that the hypegraph cannot be split into two smaller disjoint
  hypergraphs). The labelling function \(\ell\colon E \to \{+1, -1\}\)
  maps each hyperedge to a sign \(+1\) or \(-1\).
\end{definition}

We will oftenly refer to a hyperedge as a \emph{line}. In
Figure~\ref{fig:as-graph} (a), the lines going through sequences of
four vertices are the hyperedges. Similarly, in
Figure~\ref{fig:as-graph} (b), the horizontal and vertical lines
touching the sequences of three vertices are the hyperedges.  As
already mentioned, arrangements define the configurations on which
games may be played.

\begin{definition}[Classical Realization~\cite{arkhipov2012}]\label{def:classical-re}
  A classical realization of an arrangement \(A = (V, E, \ell)\) is a
  labelling \(c\colon V \to \{+1, -1\}\) that, for every hyperedge
  \(e \in E\), satisfies the property 
  \[
    \prod_{v \in e} c(v) = \ell(e).
  \]
\end{definition}

\begin{tcbexample}{Classical Realization}{class-re}
  Figure~\ref{fig:class-re} depicts an example of a classically
  realizable arrangement. That is, an arrangement for which there exists
  a classical realization.

  \begin{figure}[H]
    \begin{center}
      \begin{tikzpicture}[vertex/.style={circle, thin, fill=blue!30, draw, inner sep=0, minimum size=5pt}]
        \node (00) [vertex] at (-1.25, 0) {};
        \node (01) [vertex] at (0,  0) {};
        \node (02) [vertex] at (1.25,  0) {};

        \node (r0) [text=red!50!black!80] at (1.65, -0.05) {\(-1\)};
        \node (r1) [text=red!50!black!80] at (1.65, -1.20) {\(-1\)};

        \node (c0) [text=green!50!black!80] at (-1.2, -1.65) {\(+1\)};
        \node (c1) [text=green!50!black!80] at (-0.05, -1.65) {\(+1\)};
        \node (c2) [text=green!50!black!80] at (1.2, -1.65) {\(+1\)};

        (10) edge (11)
        (11) edge (12)
        ;
      \end{tikzpicture}
    \end{center}
    \caption{Example of a classically realizable arrangement.\label{fig:class-re}}
  \end{figure}

    A classical realization \(c\) for this arrangement is
  \begin{align*}
    c(v_{00}) = c(v_{01}) = c(v_{10}) = c(v_{11}) &= +1 \\
    c(v_{02}) = c(v_{12}) &= -1.
  \end{align*}
\end{tcbexample}

\begin{definition}[Quantum Realization~\cite{arkhipov2012}]\label{def:quantum-re}
  A quantum realization of an arrangement \(A = (V, E, \ell)\) is a
  labelling \(q\colon V \to \operatorname{GL}(\mathcal{H})\) is a
  mapping from each vertex to an observable \(M\) on a fixed
  finite-dimensional Hilbert-space \(\mathcal{H}\), such that
  \begin{itemize}
  \item \(M\) is Hermitian and squares to the identity, or
    equivalently, has eigenvalues \(\pm{}1\);

  \item For each hyperedge, the observable assigned to its vertices
    pairwise commute and

  \item For each hyperedge \(e \in E\), the labelling of its vertices
    satisfies the property
    \[
      \prod_{v \in e} q(v) = \ell(e) I.
    \]
  \end{itemize}
\end{definition}

A classical realization is simply a quantum realization in which
\(\mathcal{H} = \mathbb{R}\). As such, every classically realizable
arrangement is quantumly realizable. An example of quantum realization
was given in Section~\ref{sec:quantum-sol} for the magic square game.
Any arrangement that is quantumly realizable with observables that all
mutually commute, then it is also classically
realizable~\cite[Proposition 8]{arkhipov2012}. The proof follows by
the simultaneous diagonalization of the observables, similar to our
proof for Lemma~\ref{lem:product}.

It turns out that the existence of a classical or quantum realization
of an arrangement depends only on whether the number of \(-1\) labels
is odd or even. This is called the \emph{parity} of the arrangement.

\begin{definition}[Parity~\cite{arkhipov2012}]\label{def:parity}
  The parity \(p(\ell)\) of an arrangement \(A = (V, E, \ell)\) is
  \[
    p(\ell) = \prod_{e \in E} \ell(E),
  \]
  which is \(-1\) if there is an odd number of \(-1\) labels, or \(+1\) otherwise.
\end{definition}

If there exists a realization (either classical or quantum) of an
arrangement \(A = (V, E, \ell)\), then it is possible to construct a
realization for \(A' = (V, E, \ell')\) from the realization of
\(A\)~\cite[Propositions 10 and 12]{arkhipov2012}. Furthermore, an
arrangement is classically realizable if, and only if, its parity is
\(+1\)~\cite[Proposition 11]{arkhipov2012}. Despite this fundamental result,
Classically realizable arrangements are not as much interesting as the
quantumly ones. Therefore, the goal is to characterize the gap between
these two worlds. The arrangements that are quantumly realizable, but
are not classically realizable, are called \emph{magic} and are
defined as follows:

\begin{definition}[Magic Arrangement~\cite{arkhipov}]\label{def:magic-arr}
  An arrangement is said magic its parity is \(-1\) and it is
  quantumly realizable.
\end{definition}

The magic square and the pentagram are examples of magic arrangements.
Equipped with all these tools, we now define a generalization of \emph{parity}
pseudo-telepathy games (Mermin-style games):

\printbibliography{}
\end{document}
